Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-09-14 grove-paper.tex
Convert to PLDI format and add bibliography

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[acmsmall,review,anonymous,nonacm]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[acmsmall]{acmart}\settopmatter{}

@@

\bibliographystyle{ACM-Reference-Format}
\citestyle{acmauthoryear}

@@

\author{Cyrus Omar}
\orcid{0000-0003-4502-7971}
\affiliation{
  \position{Assistant Research Scientist}
  \department[0]{Computer Science and Engineering}
  \department[1]{Electrical Engineering and Computer Science}
  \department[2]{College of Engineering}
  \institution{University of Michigan}
  \streetaddress{Bob and Betty Beyster Building, 2260 Hayward Street}
  \city{Ann Arbor}
  \state{MI}
  \postcode{48109-2121}
  \country{USA}
}

@@

@@

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.3\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{*}_{2}$" [> "left", > "19"'] -> {
    "$\texttt{var(u)}_{12}$" [> "left", > "13"'],
    "$\texttt{var(w)}_{16}$" [> "right", > "17"']
   },
   {
    "$\texttt{var(x)}_{20}$" [> "right", > "21"']
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Alice ... TODO}
\label{fig:Multi-child-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.3\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{*}_{2}$" [> "left", > "19"'] -> {
    "$\texttt{var(u)}_{12}$" [> "left", > "13"'],
    "$\texttt{var(w)}_{16}$" [> "right", > "17"']
   },
   "$\texttt{var(y)}_{22}$" [> "right", > "23"']
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Bob ... TODO}
\label{fig:Multi-child-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.3\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{*}_{2}$" [> "left", > "19"'] -> {
    "$\texttt{var(u)}_{12}$" [> "left", > "13"'],
    "$\texttt{var(w)}_{16}$" [> "right", > "17"']
   },
   {
    "$\texttt{var(x)}_{20}$" [> "right", > "21"'],
    "$\texttt{var(y)}_{22}$" [> "right", > "23"']
   }
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Multi-child-a} with \autoref{fig:Multi-child-b}}
\label{fig:Multi-child-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-child conflicts}
\label{fig:Multi-child}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{+}_{24}$" [> "left", > "23"'] -> {
    "$\texttt{var(x)}_{26}$" [> "left", > "25"'],
    {}
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-parent-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{+}_{24}$" [> "left", > "23"'],
   "$\texttt{var(x)}_{26}$" [> "right", > "27"']
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Multi-parent-a} after Alice ... TODO}
\label{fig:Multi-parent-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{+}_{24}$" [> "left", > "23"'] -> {
    {},
    "$\texttt{var(x)}_{26}$" [> "right", > "29"']
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Multi-child-a} after Bob ... TODO}
\label{fig:Multi-parent-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  a/{$\texttt{+}_{8}$} [> "root", > "7"'] -> {
   "$\texttt{+}_{24}$" [> "left", > "23"'] ->["right", "29"'] {
    {},
    b/"$\texttt{var(x)}_{26}$"
   },
   {}
  }
 },
 a ->["right", "27"'] b
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Multi-parent-b} with \autoref{fig:Multi-parent-c}}
\label{fig:Multi-parent-d}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-parent conflicts}
\label{fig:Multi-parent}
\end{figure}

@@

\subsection{Disconnection}
\label{sub:Disconnection}

@@

Hazel

@@

Pidjul

@@

%% Appendix
\appendix
\section{Appendix}
\label{apx:Appendix}

@@

%% Bibliography
%\bibliography{bibfile}

>>>>

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[acmsmall,review,anonymous,nonacm]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
\documentclass[sigplan,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[acmsmall]{acmart}\settopmatter{}

@@

\bibliographystyle{ACM-Reference-Format}
%\citestyle{acmauthoryear}
\citestyle{acmnumeric}

@@

\author{Cyrus Omar}
\orcid{0000-0003-4502-7971}
\affiliation{
  %\position{Assistant Research Scientist}
  \department[0]{Computer Science and Engineering}
  \department[1]{Electrical Engineering and Computer Science}
  \department[2]{College of Engineering}
  \institution{University of Michigan}
  \streetaddress{Bob and Betty Beyster Building, 2260 Hayward Street}
  \city{Ann Arbor}
  \state{MI}
  \postcode{48109-2121}
  \country{USA}
}

@@

TODO: PLDI: two column format

@@

TODO: have star or dot dot arrows for skipping steps

Arrow coming from 5b to 6a and 6b

Diamond diagram referencing diagrams

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.3\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{*}_{2}$" [> "left", > "19"'] -> {
    "$\texttt{var(u)}_{12}$" [> "left", > "13"'],
    "$\texttt{var(w)}_{16}$" [> "right", > "17"']
   },
   {
    "$\texttt{var(x)}_{20}$" [> "right", > "21"']
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Alice ... TODO}
\label{fig:Multi-child-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.3\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{*}_{2}$" [> "left", > "19"'] -> {
    "$\texttt{var(u)}_{12}$" [> "left", > "13"'],
    "$\texttt{var(w)}_{16}$" [> "right", > "17"']
   },
   "$\texttt{var(y)}_{22}$" [> "right", > "23"']
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Bob ... TODO}
\label{fig:Multi-child-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.3\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{*}_{2}$" [> "left", > "19"'] -> {
    "$\texttt{var(u)}_{12}$" [> "left", > "13"'],
    "$\texttt{var(w)}_{16}$" [> "right", > "17"']
   },
   {
    "$\texttt{var(x)}_{20}$" [> "right", > "21"'],
    "$\texttt{var(y)}_{22}$" [> "right", > "23"']
   }
  }
 }
};
\end{tikzpicture}

TODO: show UI
\caption{The result of merging \autoref{fig:Multi-child-a} with \autoref{fig:Multi-child-b}}
\label{fig:Multi-child-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-child conflicts}
\label{fig:Multi-child}
\end{figure}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{+}_{24}$" [> "left", > "23"'] -> {
    "$\texttt{var(x)}_{26}$" [> "left", > "25"'],
    {}
   },
   {}
  }
 }
};
\end{tikzpicture}

TODO: use * and +

TODO: UI (at least moc up)
\caption{Initial code}
\label{fig:Multi-parent-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{+}_{24}$" [> "left", > "23"'],
   "$\texttt{var(x)}_{26}$" [> "right", > "27"']
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Multi-parent-a} after Alice ... TODO}
\label{fig:Multi-parent-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "root", > "7"'] -> {
   "$\texttt{+}_{24}$" [> "left", > "23"'] -> {
    {},
    "$\texttt{var(x)}_{26}$" [> "right", > "29"']
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Multi-child-a} after Bob ... TODO}
\label{fig:Multi-parent-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  a/{$\texttt{+}_{8}$} [> "root", > "7"'] -> {
   "$\texttt{+}_{24}$" [> "left", > "23"'] ->["right", "29"'] {
    {},
    b/"$\texttt{var(x)}_{26}$"
   },
   {}
  }
 },
 a ->["right", "27"'] b
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Multi-parent-b} with \autoref{fig:Multi-parent-c}}
\label{fig:Multi-parent-d}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-parent conflicts}
\label{fig:Multi-parent}
\end{figure}

@@

\subsubsection{Disconnection}
\label{sub:Disconnection}

@@

Hazel
\citep{Omar:2019:10.1145/3290327}

@@

Operational Transforms

Pijul

@@

%% Appendix
\appendix

%% Appendixes that will be published  go **BEFORE** the bibliography and count towards the page count
\section{Appendix}
\label{apx:Appendix}

@@

%% Bibliography
\bibliography{grove-paper}

%% Temporary appendixes that will not be published go **AFTER** the bibliography and do not count towards the page count
